
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Vishnuhari V A} \\ \vspace{1pt}
    \small 8590449717 $|$ \href{mailto:vishnuhari17@ieee.org}{\underline{vishnuhari17@ieee.org}} $|$ 
    \href{https://www.linkedin.com/in/vishnuhari17/}{\underline{https://www.linkedin.com/in/vishnuhari17/}} $|$
    \href{https://github.com/vishnuhari17}{\underline{https://github.com/vishnuhari17}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Federal Institute of Science and Technology (FISAT)}{Kerala, India}
      {B.Tech - Computer Science and Engineering}{2022 - 2026 (Expected)}

    \resumeSubheading
      {Bharathiya Vidya Bhavan, Kodungallur}{Kerala, India}
      {12th Grade CBSE}{2020 - 2022}

    \resumeSubheading
      {Bharathiya Vidya Bhavan, Kodungallur}{Kerala, India}
      {10th Grade CBSE}{2019 - 2020}

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full Stack Developer}{Jan 2025 - Mar 2025}
      {Lylhelp}{Kerala, India}
      \resumeItemListStart

        \resumeItem{Designed and implemented a WhatsApp messaging template for personalized communications, enhancing customer engagement.}

        \resumeItem{Collaborated with a cross-functional team to develop backend features, ensuring seamless integration across platforms.}

    \resumeItemListEnd

    \resumeSubheading
      {Full Stack Angular Developer}{Dec 2024 - Jan 2025}
      {Nest Digital Kakkanad}{Kochi, India}
      \resumeItemListStart

        \resumeItem{Engineered five fully-functional Angular web applications, enhancing user experience and reducing latency.}

        \resumeItem{Collaborated on API creation, providing robust backend support for frontend functionalities.}

    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Prathibhimb AI} $|$ \emph{FastAPI, React, Vite, Recharts, ChatGPT API}}{2023}
          \resumeItemListStart

            \resumeItem{Developed an AI-powered chart generation tool delivering dynamic visualizations in under 2 minutes.}

            \resumeItem{Streamlined processes, reducing chart creation time by 92\% through automated workflows.}

          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Food Redistribution System} $|$ \emph{Flutter, Firebase}}{2023}
          \resumeItemListStart

            \resumeItem{Created a Flutter-based application facilitating surplus food redistribution, connecting 100+ events organizers.}

            \resumeItem{Leveraged location-based technologies to reduce food wastage by 75\%.}

          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Certificate Generation \& Verification System} $|$ \emph{Python, Next.js, MongoDB, Express}}{2023}
          \resumeItemListStart

            \resumeItem{Automated and digitized the process for creating and verifying certificates, cutting paperwork by 65\%.}

            \resumeItem{Implemented name-based search and QR code functionality, enhancing efficiency by reducing manual verification time by 95\%.}

          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Disaster Management System} $|$ \emph{Flutter, Firebase}}{2023}
          \resumeItemListStart

            \resumeItem{Engineered a real-time alert app with geofencing notifications, improving emergency response times by 30\%.}

            \resumeItem{Facilitated user-generated alerts to provide immediate and accurate disaster updates.}

          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Student Support Bot} $|$ \emph{Express, PostgreSQL, Telegram API}}{2023}
          \resumeItemListStart

            \resumeItem{Developed a Telegram bot managing notes, assignments, and queries through a PostgreSQL database.}

            \resumeItem{Optimized admin and user roles, reducing manual tasks by 80\% and enhancing student resource accessibility.}

          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, Java, Dart, C, HTML, CSS} \\
     \textbf{Frameworks}{: React, Next.js, Tailwind CSS, Material-UI, Flutter} \\
     \textbf{Developer Tools}{: Git/GitHub, Docker, AWS, Vercel, Netlify, ChatGPT API, Gemini, Huggingface} \\
     \textbf{Libraries}{: Recharts, Express, Flutter}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
